Dual-Mode PSK Transceiver on SDR With FPGA

### 2024-01-06 latex/paper.tex
ILA Data Processing Using Python
Downsample ILA Data by 2 In TikZ

    \subsection{BPSK-Mode Receiver}

    \subsection{QPSK-Mode Receiver}

@@

@@

>>>>

    \subsection{Carrier Synchronization Convergence}

@@

    \begin{figure*}
      \setlength{\tabcolsep}{2pt}
      \newcommand\Modulation{BPSK}%
      \newcommand\IsBPSK1%
      \subfloat[A \Modulation{} packet.]{%
        \sffamily\notsotiny
        \begin{tabularx}{\linewidth}{@{}lX@{}}
          DAC\_I[11:0] & \input{tikz/ila/DAC_I} \\
          DAC\_Q[11:0] & \input{tikz/ila/DAC_Q} \\
          ADC\_I[11:0] & \input{tikz/ila/ADC_I} \\
          ADC\_Q[11:0] & \input{tikz/ila/ADC_Q} \\
          I\_16M[15:0] & \input{tikz/ila/I_16M} \\
          Q\_16M[15:0] & \input{tikz/ila/Q_16M} \\
          I\_1M[15:0] & \input{tikz/ila/I_1M} \\
          Q\_1M[15:0] & \input{tikz/ila/Q_1M} \\
        \end{tabularx}%
      }\\
      \renewcommand\Modulation{QPSK}%
      \renewcommand\IsBPSK0%
      \subfloat[A \Modulation{} packet.]{%
        \sffamily\notsotiny
        \begin{tabularx}{\linewidth}{@{}lX@{}}
          DAC\_I[11:0] & \input{tikz/ila/DAC_I} \\
          DAC\_Q[11:0] & \input{tikz/ila/DAC_Q} \\
          ADC\_I[11:0] & \input{tikz/ila/ADC_I} \\
          ADC\_Q[11:0] & \input{tikz/ila/ADC_Q} \\
          I\_16M[15:0] & \input{tikz/ila/I_16M} \\
          Q\_16M[15:0] & \input{tikz/ila/Q_16M} \\
          I\_1M[15:0] & \input{tikz/ila/I_1M} \\
          Q\_1M[15:0] & \input{tikz/ila/Q_1M} \\
        \end{tabularx}%
      }
      \caption{System ILA results.}
    \end{figure*}

@@

    \begin{figure*}
      \includegraphics[width=\linewidth]{../schematic/top.pdf}
      \caption{Top block diagram.}
    \end{figure*}
